### 2019-03-18 papers.tex
Import corresponding to reviews-2019 tag
papers.tex: Fix inconsistent paper title case

\addtrack
	{}{Gamification}
\addpaper
	{Aumann agreement by combat}
	{Travis Hance}
	{Keywords: Aumann agreement, combat, agents}
	{SIGBOVIK_2019_paper_18}
	{0cm}
	{}
\addpaper
	{Monetization of development tools for fun and profit}
	{Albin Eldstål-Damlin}
	{Keywords: monetization, micro-transactions, free-to-play, gamification}
	{SIGBOVIK_2019_paper_1}
	{0cm}
	{}

@@

\addtrack
	{}{Machine learning}
\addpaper
	{Color- and piece-blind chess}
	{Dr.\@ Tom Murphy VII Ph.D.}
	{Keywords: chess, handicaps, man-in-the-middle attacks, neural networks}
	{SIGBOVIK_2019_paper_36}
	{0cm}
	{}
\addpaper
	{Dimensionality-reducing encoding for classification of Pythagorean engendered numbers}
	{Rany Tith and Oscar I.\@ Hernandez}
	{Keywords: number theory, machine learning, encoding, information theory, classification, gender theory, integers, globalization, computation, mathematics}
	{SIGBOVIK_2019_paper_28}
	{0cm}
	{}
\addpaper
	{emojizip: A text compression system based on pictogram-kiloword equivalence}
	{William Gunther and Brian Kell}
	{Keywords: data compression, TensorFlow, [laughing crying emoji]}
	{SIGBOVIK_2019_paper_39}
	{0cm}
	{}
\addpaper
	{Meta-meta-learning for neural architecture search through arXiv Descent}
	{Antreas Antoniou \textit{et al.}}
	{Keywords: meta, meta-meta, deep, NAS}
	{SIGBOVIK_2019_paper_11}
	{0cm}
	{}
\addpaper
	{Towards automatic low hanging fruit identification for the steering of ML research}
	{Nick Frosst and Aidan Gomez}
	{Keywords: machine learning, detection, segmentation, orientation, apple, akee, apricot, avocado, banana, bilberry, blackberry, blackcurrant, black sapote, blueberry, boysenberry, Buddha's hand (fingered citron), crab apples, currant, cherry, cherimoya (custard apple), chico fruit, cloudberry, coconut, cranberry, cucumber, damson, date, dragonfruit (or pitaya), durian, elderberry, feijoa, fig, goji berry, gooseberry, grape, raisin, grapefruit, guava, honeyberry, huckleberry, jabuticaba, jackfruit, jambul, japanese plum, jostaberry, jujube, juniper berry, kiwano (horned melon), kiwifruit, kumquat, lemon, lime, loquat, longan, lychee, mango, mangosteen, marionberry, melon, cantaloupe, honeydew, watermelon, miracle fruit, mulberry, nectarine, nance, olive, orange, blood orange, clementine, mandarine, tangerine, papaya}
	{SIGBOVIK_2019_paper_32}
	{0cm}
	{}

@@

\addtrack
	{}{Chess}
\addpaper
	{Is ``Dicong Qiu. Is this the shortest SIGBOVIK paper? From 2018 SIGBOVIK paper'' the shortest SIGBOVIK paper?}
	{Thomas Bach}
	{Keywords: o, o, o}
	{SIGBOVIK_2019_paper_14}
	{0cm}
	{}
\addpaper
	{Is this the tiniest SIGBOVIK paper ever?}
	{Mitchell Jones}
	{Keywords: tiny, zoom, Fermat}
	{SIGBOVIK_2019_paper_5}
	{0cm}
	{}
\addpaper
	{No, this is the tiniest SIGBOVIK paper ever.}
	{Patrick Lin}
	{Keywords: tony, zoom, Mitchell, heart}
	{SIGBOVIK_2019_paper_6}
	{0cm}
	{}
\addpaper
	{Revisiting the shortest SIGBOVIK paper / The revised shortest SIGBOVIK paper}
	{Richard Wardin}
	{Keywords: word golf, revisioned paper, deflation}
	{SIGBOVIK_2019_paper_9}
	{0cm}
	{}

@@

\addtrack
	{}{Error-correcting codes}
\addpaper
	{On double-sided QR codes}
	{Alexey Tikhonov}
	{Keywords: QR codes, steganography, error correction, high capacity, high density, robustness}
	{SIGBOVIK_2019_paper_2}
	{0cm}
	{}
\addpaper
	{Novel defense against code theft using properties of Fibonacci series}
	{Sayan Chaudhry}
	{Keywords: indent, code style, Fibonacci, plagiarism}
	{SIGBOVIK_2019_paper_20}
	{0cm}
	{}
\addpaper
	{Error-detecting RLIRFO data structures for the win}
	{Darío de la Fuente García, Félix Áxel Gimeno Gil, and Juan Carlos Morales Vega}
	{Keywords: error detection, data structures, cosmic rays, stacks, stacks of stacks, stacks of stacks of stacks, template metaprogramming}
	{SIGBOVIK_2019_paper_25}
	{0cm}
	{}

\addtrack
	{}{Measurement studies}
\addpaper
	{Applications of Standard ML at Google}
	{Andrew Benson}
	{Keywords: SML, Standard ML, one-fifty, Harper, Google, software engineering, programming languages}
	{SIGBOVIK_2019_paper_19}
	{0cm}
	{}
\addpaper
	{93\% of Paint Splatters are Valid Perl Programs}
	{Colin McMillen and Tim Toady}
	{Keywords: perl, OCR, regret}
	{SIGBOVIK_2019_paper_34}
	{0cm}
	{}

>>>>

\addtrack
	{}{Gamification}
\addpaper
	{Aumann agreement by combat}
	{Travis Hance}
	{Keywords: Aumann agreement, combat, agents}
	{SIGBOVIK_2019_paper_18}
	{0cm}
	{}
\addpaper
	{Monetization of development tools for fun and profit}
	{Albin Eldstål-Damlin}
	{Keywords: monetization, micro-transactions, free-to-play, gamification}
	{SIGBOVIK_2019_paper_1}
	{0cm}
	{}
\addreview{SIGBOVIK_2019_review_1}{0cm}

@@

\addtrack
	{}{Machine learning}
\addpaper
	{Color- and piece-blind chess}
	{Dr.\@ Tom Murphy VII Ph.D.}
	{Keywords: chess, handicaps, man-in-the-middle attacks, neural networks}
	{SIGBOVIK_2019_paper_36}
	{0cm}
	{}
\addpaper
	{Dimensionality-reducing encoding for classification of Pythagorean engendered numbers}
	{Rany Tith and Oscar I.\@ Hernandez}
	{Keywords: number theory, machine learning, encoding, information theory, classification, gender theory, integers, globalization, computation, mathematics}
	{SIGBOVIK_2019_paper_28}
	{0cm}
	{}
\addpaper
	{emojizip: A text compression system based on pictogram-kiloword equivalence}
	{William Gunther and Brian Kell}
	{Keywords: data compression, TensorFlow, [laughing crying emoji]}
	{SIGBOVIK_2019_paper_39}
	{0cm}
	{}
\addreview{SIGBOVIK_2019_review_39}{0cm}
\addpaper
	{Meta-meta-learning for neural architecture search through arXiv Descent}
	{Antreas Antoniou \textit{et al.}}
	{Keywords: meta, meta-meta, deep, NAS}
	{SIGBOVIK_2019_paper_11}
	{0cm}
	{}
\addpaper
	{Towards automatic low hanging fruit identification for the steering of ML research}
	{Nick Frosst and Aidan Gomez}
	{Keywords: machine learning, detection, segmentation, orientation, apple, akee, apricot, avocado, banana, bilberry, blackberry, blackcurrant, black sapote, blueberry, boysenberry, Buddha's hand (fingered citron), crab apples, currant, cherry, cherimoya (custard apple), chico fruit, cloudberry, coconut, cranberry, cucumber, damson, date, dragonfruit (or pitaya), durian, elderberry, feijoa, fig, goji berry, gooseberry, grape, raisin, grapefruit, guava, honeyberry, huckleberry, jabuticaba, jackfruit, jambul, japanese plum, jostaberry, jujube, juniper berry, kiwano (horned melon), kiwifruit, kumquat, lemon, lime, loquat, longan, lychee, mango, mangosteen, marionberry, melon, cantaloupe, honeydew, watermelon, miracle fruit, mulberry, nectarine, nance, olive, orange, blood orange, clementine, mandarine, tangerine, papaya}
	{SIGBOVIK_2019_paper_32}
	{0cm}
	{}

@@

\addtrack
	{}{Chess}
\addpaper
	{Is ``Dicong Qiu. Is this the shortest SIGBOVIK paper? From 2018 SIGBOVIK paper'' the shortest SIGBOVIK paper?}
	{Thomas Bach}
	{Keywords: o, o, o}
	{SIGBOVIK_2019_paper_14}
	{0cm}
	{}
\addpaper
	{Is this the tiniest SIGBOVIK paper ever?}
	{Mitchell Jones}
	{Keywords: tiny, zoom, Fermat}
	{SIGBOVIK_2019_paper_5}
	{0cm}
	{}
\addpaper
	{No, this is the tiniest SIGBOVIK paper ever.}
	{Patrick Lin}
	{Keywords: tony, zoom, Mitchell, heart}
	{SIGBOVIK_2019_paper_6}
	{0cm}
	{}
\addpaper
	{Revisiting the shortest SIGBOVIK paper / The revised shortest SIGBOVIK paper}
	{Richard Wardin}
	{Keywords: word golf, revisioned paper, deflation}
	{SIGBOVIK_2019_paper_9}
	{0cm}
	{}
\addreview{SIGBOVIK_2019_review_9}{0cm}

@@

\addtrack
	{}{Error-correcting codes}
\addpaper
	{On double-sided QR codes}
	{Alexey Tikhonov}
	{Keywords: QR codes, steganography, error correction, high capacity, high density, robustness}
	{SIGBOVIK_2019_paper_2}
	{0cm}
	{}
\addreview{SIGBOVIK_2019_review_2}{0cm}
\addpaper
	{Novel defense against code theft using properties of Fibonacci series}
	{Sayan Chaudhry}
	{Keywords: indent, code style, Fibonacci, plagiarism}
	{SIGBOVIK_2019_paper_20}
	{0cm}
	{}
\addpaper
	{Error-detecting RLIRFO data structures for the win}
	{Darío de la Fuente García, Félix Áxel Gimeno Gil, and Juan Carlos Morales Vega}
	{Keywords: error detection, data structures, cosmic rays, stacks, stacks of stacks, stacks of stacks of stacks, template metaprogramming}
	{SIGBOVIK_2019_paper_25}
	{0cm}
	{}

\addtrack
	{}{Measurement studies}
\addpaper
	{Applications of Standard ML at Google}
	{Andrew Benson}
	{Keywords: SML, Standard ML, one-fifty, Harper, Google, software engineering, programming languages}
	{SIGBOVIK_2019_paper_19}
	{0cm}
	{}
\addpaper
	{93\% of paint splatters are valid Perl programs}
	{Colin McMillen and Tim Toady}
	{Keywords: perl, OCR, regret}
	{SIGBOVIK_2019_paper_34}
	{0cm}
	{}
